\textls[-0]{\thetitle}

### 2023-03-25 canonicitymodel.tex
One more colorbox for help parsing.

\begin{align*}
  \denotesC{\goodSig{\Gm}{\lsig}{n}} & \text{ is a list of 3-tuple of length $n$  } \\
  % & \text{ and we define  } {\goodSigC{\Gm}{\lsig}{n}} :\iff \denotesC{\goodSig{\Gm}{\lsig}{n}} \text{ is defined} \\ 
  \denotesC{\goodWSigU{j}{\Gm}{\wsig}{n}} &: \GMWSig{j}{\denotesCC{\Gm}}{n} \\ 
    &\text{ i.e., a list of 2-tuple of length $n$ } \\
  % & \text{ and we define } \goodWSigC{\Gm}{\wsig}{n} :\iff \denotesC{\goodWSig{\Gm}{\tau}{n}} \text{ is defined} \\
  \text{we define }\TyLkg{}, \TyTkg{} & \text{ inductively on its input signature, via } \mathit{L},\Glued{\mathit{P}}  \\ 
  \mathit{L}("nil") &=  \denotesC{\top}  \\
  \mathit{L}((A,s,T) :: tl)(\gm)(\gm')(t) &= {\mathit{L}(tl)}(\gm)(\gm')(\lkgproj{1}{t}) \times \Gmodel{\GluedPi{A}{T}}(\gm)(\gm')(\lam{\lkgproj{2}{t}})   \\
  \Glued{\mathit{P}}("nil") &= ( \TyTkg{\LSigEmp} , \denotesC{\top} )\\
  \Glued{\mathit{P}}((A,s,T) :: tl) &= \Glued{\Sigma}(\Glued{\mathit{P}}(tl), \Gsub{T}{\GSubstExt{{\GSubstWeak{1}}}{s}}) \quad \text{(doing substitution on $T$)} \\
  \denotesC{\goodType{\Gm}{\TyLkg{\lsig}}{}} &= {\mathit{L}(\denotesC{\lsig})} \\
  \denotesC{\goodType{\Gm}{\TyTkg{\lsig}}{}} &= \Gmodel{\Glued{\mathit{P}}(\denotesC{\lsig})} \quad \text{ discard syntax info}  \\
  % 
  \denotesC{\goodSig{\Gm}{\LSigEmp}{0}} &= "nil"\\ 
  \denotesC{\goodSig{\Gm}{\LSigAdd{\lsig}{s}{T}}{n+1}} &= (\denotesCC{A}, \denotesCC{s}, \denotesCC{T})::\denotesC{\lsig} \quad \text{ given } \goodTerm{\Gm, \TyTkg{\lsig}}{s}{A} \\ 
  \denotesC{\goodSig{\Gm}{\sub{\lsig}{\gm}}{n}} & \text{ is done by point-wise/component-wise substitution} \\
  \denotesC{\goodSig{\Gm}{\lsigproj{1}{\lsig}}{n}} &= "tl"~\denotesC{\lsig}\\ 
  \denotesC{\goodType{\Gm}{\lsigprojT{\lsig}}{}} &= \Gmodel{("hd"~\denotesC{\lsig})[0]} \quad \text{ take the first element in the tuple,...}\\ 
  \denotesC{\goodTerm{\Gm, \TyTkg{\lsigproj{1}{\lsig}}}{\lsigproj{s}{\lsig}}{\lsigprojT{\lsig}}} &= \Gmodel{("hd"~\denotesC{\lsig})[1]} \quad \text{  ... and discard syntax}\\ 
  \denotesC{\goodType{\Gm, \lsigprojT{\lsig}}{\lsigproj{2}{\lsig}}{}} &= \Gmodel{("hd"~\denotesC{\lsig})[2]}\\
  \denotesC{\goodTerm{\Gm}{\LkgEmp}{\TyLkg{\LSigEmp}}} &= \denotesC{\unit} \\
  \denotesC{\goodTerm{\Gm}{\LkgAdd{\lkg}{t}}{\TyLkg{\LSigAdd{\lsig}{s}{T}}}}(\gm)(\gm') &= (\denotesC{\lkg}(\gm)(\gm') , \Gmodel{\Glam{\denotesCC{t}}}(\gm)(\gm')) \\
  \denotesC{\goodTerm{\Gm}{\Tkg{\lkg}}{\TyTkg{\lsig}}} &= \denotesC{\unit}
  \quad \text{ when \goodSig{\Gm}{\lsig}{0}} \\
  \denotesC{\goodTerm{\Gm}{\Tkg{\lkg}}{\TyTkg{\lsig}}} &= \Gmodel{\Gpair{\Glued{\ell'}}{
    \colorbox{blue!17}{\Gsub{
    \colorbox{blue!9}{\Gsub{
    \colorbox{blue!1}{\denotesCC{\lkgproj{2}{\lkg}}}
    }{\GSubstExt{{\GSubstWeak{1}}}{s}}}
    }{\GSubstExt{\Glued{("id")}}{ \Glued{\ell'} }}}
    }}
  \\ &\text{ where } \Glued{\ell'} = \denotesCC{\Tkg{\lkgproj{1}{\lkg}}} 
  \\ &\text{ when } \denotesC{\goodSig{\Gm}{\lsig}{n+1}} = (A, s, T)::\_ \\ 
\end{align*}
This is the first point our proof becomes cryptic because of this bullet notation.

The first complexity comes from the three ``bullets after comma'' notation. The way to interpret this notation is that, this ``$\GSubstExt{\_}{\_}$'' should be considered as a binary function requiring two input of glued interpretation.

However, a careful reader will notice that, because of the overloading of the notation of dependent tuple construction and substitution extension, our glued notation is also overloading. The first one ``$\Gpair{\Glued{\ell'}}{...}$'' should be the glued interpretation for dependent tuple, but the other two should be the one for substitution extension.

Similarly, the second complexity comes from the bullets after the square bracket, which as expected, is the glued interpretation for substitution. Again, ``$\Gsub{\_}{\_}$'' should be considered as a binary function consuming two glued interpretation, corresponding to the substitution operation ``$\sub{\_}{\_}$''.

Also note that, the only non-bullet-upscripted $s$ is from the pattern matching of the interpretation of $\lsig$.

In all, the whole interpretation should be considered as:
\begin{enumerate}
  \item We first get $\denotesCC{\lkgproj{2}{\lkg}}$, the glued interpretation of the projection of the linkage 
  \item Then we apply it with two substitution,  $\Gsub{\_}{\GSubstExt{{\GSubstWeak{1}}}{s}}$ and $\Gsub{\_}{\GSubstExt{\Glued{("id")}}{ \Glued{\ell'} }}$
  \item Then we use glued interpretation of dependent tuple to combine it with $\Gpair{\Glued{\ell'}}{\_}$
\end{enumerate}

To reflect that, we use background colour to help parsing for the proof, and there is no meaning for the choice of colour.

\begin{align*}
  \denotesC{\goodTerm{\Gm}{\lkgproj{1}{\lkg}}{\TyLkg{\lsig}}}(\gm)(\gm') &= \denotesC{\ell}(\gm)(\gm')[0] \quad \text{ take the first element in the tuple} \\
  \denotesC{\goodTerm{\Gm, \lsigprojT{\lsig}}{\lkgproj{2}{\lkg}}{T}}(\gm_+)(\gm_+') &= ((\denotesC{\ell}(\pi_1{\gm_+})(\gm_+'[0]))[1])(\pi_2{\gm_+})(\gm_+'[1]) \\
  \denotesC{\goodWSig{\Gm}{\WSigEmp}{0}} &= "nil" \\
  \denotesC{\goodWSig{\Gm}{\WSigAdd{\wsig}{A}{B}}{n+1}} &= (\denotesCC{A} , \denotesCC{B}) :: \denotesC{\wsig}\\
  \denotesC{\goodWSig{\Gm}{\sub{\wsig}{\gm}}{n}} & \text{ is done by point-wise/component-wise substitution} \\
  \denotesC{\goodType{\Gm}{\wsigproj{j}{1}{\wsig}}{}} &= \Gmodel{(\text{ $j$-th element of }~\denotesC{\wsig})[0]}\\
  \denotesC{\goodType{\Gm, \wsigproj{j}{1}{\wsig}}{\wsigproj{j}{2}{\wsig}}{}} &= \Gmodel{(\text{ $j$-th element of }~\denotesC{\wsig})[1]}\\
  \denotesC{\goodWSig{\Gm}{\WSigSub{\wsig}}{n}} &= "tl"~\denotesC{\wsig}\\
  \denotesC{\goodTerm{\Gm}{\wcode{\wsig}}{\cU}}(\gm)(\gm')(t) &= \CWmodel~(\Gsub{\denotesCC{\wsig}}{\Glued{\gm}})~t \\
  \denotesC{\goodTerm{\Gm}{\Wsup{i}{\wsig}{a}{b}}{\El{\wcode{\wsig}}}}(\gm)(\gm') &= \CWsup~i~
  \colorbox{blue!10}{(\Gsub{\denotesCC{a}}{\Glued{\gm}})}~
  \colorbox{green!10}{(\Gsub{\denotesCC{b}}{{\Glued{\gm^\uparrow}}})} \\
  % CsTy~A~B~R &= {\GluedPi{A}{\GluedPi {\GluedPi{B}{\Gsub{R}{\GSubstWeak{2}}}} {\Gsub{R}{\GSubstWeak{2}}}}} \\
  \denotesC{\goodType{\Gm}{\CaseSig{"A"}{"B"}{"R"}}{}} &= 
  \Gmodel{\GluedPi{\denotesCC{"A"}}{\GluedPi {\GluedPi{\denotesCC{"B"}}{\Gsub{\denotesCC{"R"}}{\GSubstWeak{2}}}} {\Gsub{\denotesCC{"R"}}{\GSubstWeak{2}}}}} \\
  % CsTy~\denotesC{A}~\denotesC{B}~\denotesC{R}\\
\end{align*}
We note that, the interpretation of $\Wsup{i}{\wsig}{a}{b}$ is defined by $\CWsup$ (defined below) will take three elements, $i$, a glued $(\Gsub{\denotesCC{a}}{\Glued{\gm}})$ and a glued $(\Gsub{\denotesCC{b}}{{\Glued{\gm^\uparrow}}})$.  As we mentioned earlier, $\Glued{\gm}$ is the equivalent form of $(\gm, \gm')$.

@@

\begin{align*}
  \text{we define } \RecSig{}{} &\text{ by induction on the signature, via } RS \\
  RS~"nil"~R &= \denotesCC{\LSigEmp} \\
  RS~((A, B) :: tl)~R &= \GLSigAdd{RS~tl~R}{\Glued{\pi_2}}{\GCaseSig{A}{B}{R}} \\ 
  \denotesC{\goodType{\Gm}{\RecSig{\wsig}{"R"}}{}} &= \Gmodel{RS~\denotesC{\tau}~\denotesC{"R"}} \\
  \denotesC{\Recproj{j}{\lkg}} &= \text{ take the $j$-th field from } \lkg 
\end{align*}
\begin{align*}
  \denotesC{\goodTerm{\Gm}{\Wrec{\wsig}{\lkg}{t}}{T}}(\gm)(\gm') = \CWrec \quad &\Gsub{\denotesCC{\wsig}}{\Glued{\gm}} \\ 
  & (\lambda w. \denotesC{"R"}(\gm)(\gm')(\Wrec{\sub{\wsig}{\gm}}{\sub{\lkg}{\gm}}{w}))\\
  &f^r\\ &\sub{t}{\gm}\\ 
  &(\denotesC{t}(\gm)(\gm')) 
\end{align*}
\begin{align*}  
  \text{ where } \quad f^r~j~\Glued{a}~b~b^c &= 
  \texttt{let}~\Glued{\rho}  \in \GTm{
    \colorbox{blue!15}{(\Glued{\cdot} \Glued{,} \colorbox{blue!5}{\Gsub{\Glued{B}}{\GSubstExt{\Glued{"id"}}{\Glued{a}}}})}
    }{
      \colorbox{green!10}{(\Gsub{\Gsub{\Glued{R}}{\Glued{\gm}}}{\GSubstWeak{1}})}
    } 
  \\
  &\texttt{ s.t.}~\Glued{\rho} \coloneq (\Wrec{\wsig}{\sub{\lkg}{\SubstComp{\gm}{\SubstWeak{1}}}}{b},b^c)~\texttt{ in } \\
  & \Gmodel{\Gsub{\Gapp{\Gsub{\Gapp{\GRecproj{j}{\Gsub{\denotesCC{\lkg}}{\Glued{\gm}}}}}{\GSubstExt{\GSubstId}{\Glued{a}}}}}{\GSubstExt{\GSubstId}{\Glam{\Glued{\rho}}}}}(\epsilon)(\star) \\
  & \quad 
   \text{ given } \goodTerm{\Gm}{\lkg}{\RecSig{\wsig}{"R"}} \\
   & \quad \text{ where }\Glued{R} = \denotesCC{"R"}, \Glued{B} = \Gwsigproj{j}{2}{\denotesCC{\wsig}}
\end{align*}

The semantic interpretations above are defined together with the following inductively defined indexed set $\CWmodel$ (with only one constructor $\CWsup$)
%
\begin{align*}
  "Inductive"~\CWmodel &: (\Glued{\wsig} \in \GWSig{i}{\denotesCC{\cdot}}{N}) \to \{ t : \goodTerm{\cdot}{t}{\El{\wcode{\wsig}}} \} \to \Set{i + 1} \quad "where" \\
    \CWsup &: j < N \to \Glued{a} \in \GTm{\Glued{\cdot}}{\Gwsigproj{j}{1}{\Glued{\wsig}}} \\
    & \to \Glued{b} \in (\GTm{
      \colorbox{blue!10}{(\Glued{\cdot} \Glued{,} \Gsub{\Gwsigproj{j}{2}{\Glued{\wsig}}}{\SubstExt{\GSubstId}{\Glued{a}}})} 
      }{
        \colorbox{green!10}{\Gsub{\GEl{\Gwcode{\Glued{\wsig}}}}{\GSubstWeak{1}}}
        }) \\
    & \to \CWmodel~\Glued{\wsig}~\Wsup{j}{\wsig}{a}{b}
\end{align*}
and its eliminator $\CWrec$
\begin{align*}
  \CWrec \  &: (\Glued{\wsig} \in \GWSig{i}{\denotesCC{\cdot}}{N}) \to 
    (P : \{ t : \goodTerm{\cdot}{t}{\El{\wcode{\wsig}}} \} \to \Set{k})  \\
    & \to 
    [j < N \to  \Glued{a} \in \GTm{\Glued{\cdot}}{\Gwsigproj{j}{1}{\Glued{\wsig}}} \\ 
    & \quad \quad \to 
    \setc{b}{\goodTerm{({\cdot} , 
    \colorbox{blue!10}{\sub{\wsigproj{j}{2}{{\wsig}}}{\SubstExt{"id"}{{a}}}}
    ) }{b}{\sub{\El{\wcode{\wsig}}}{\SubstWeak{1}}}} \\ 
    & \quad \quad \to  \prod_{\Glued{\gm} \in \GSub{\Glued{\cdot}}{(\Glued{\cdot} \Glued{,} 
    \colorbox{blue!10}{\sub{\Gwsigproj{j}{2}{\Glued{\wsig}}}{\GSubstExt{\GSubstId}{\Glued{a}}}} )}} P~(\sub{b}{ \gm }) \\
    & \quad \quad \to P~(\Wsup{j}{\wsig}{a}{b}) ] \quad \text{ (square bracket here just to make things readable)} \\
    & \to \goodTerm{\cdot}{t}{\El{\wcode{\wsig}}} \to \CWmodel~\Glued{\wsig}~t \to P~t \\
  \CWrec \  & \Glued{\wsig}~P~f~t~(\CWsup~\Glued{a}~\Glued{b}) = f~\Glued{a}~b~(\lambda \Glued{\gm}. \CWrec~\Glued{\wsig}~P~f~(\sub{b}{\gm})~(\Gmodel{\Glued{b}}~\Glued{\gm}))
\end{align*}

>>>>

  \denotesC{\goodSig{\Gm}{\lsig}{n}} & \text{ is a list of 3-tuple of length $n$  } \\
  % & \text{ and we define  } {\goodSigC{\Gm}{\lsig}{n}} :\iff \denotesC{\goodSig{\Gm}{\lsig}{n}} \text{ is defined} \\ 
  \denotesC{\goodWSigU{j}{\Gm}{\wsig}{n}} &: \GMWSig{j}{\denotesCC{\Gm}}{n} \\ 
    &\text{ i.e., a list of 2-tuple of length $n$ } \\
  % & \text{ and we define } \goodWSigC{\Gm}{\wsig}{n} :\iff \denotesC{\goodWSig{\Gm}{\tau}{n}} \text{ is defined} \\
  \text{we interpret }\TyLkg{}, \TyTkg{} & \text{ by induction on the input linkage signature, via } \mathit{L} \text{ and } \Glued{\mathit{P}}  \\ 
  \mathit{L}("nil") &=  \denotesC{\top}  \\
  \mathit{L}((A,s,T) :: tl)(\gm)(\gm')(t) &= {\mathit{L}(tl)}(\gm)(\gm')(\lkgproj{1}{t}) \times \Gmodel{\GluedPi{A}{T}}(\gm)(\gm')(\lam{\lkgproj{2}{t}})   \\
  \Glued{\mathit{P}}("nil") &= ( \TyTkg{\LSigEmp} , \denotesC{\top} )\\
  \Glued{\mathit{P}}((A,s,T) :: tl) &= \Glued{\Sigma}(\Glued{\mathit{P}}(tl), \Gsub{T}{\GSubstExt{{\GSubstWeak{1}}}{s}}) \quad \text{(doing substitution on $T$)} \\
  \denotesC{\goodType{\Gm}{\TyLkg{\lsig}}{}} &= {\mathit{L}(\denotesC{\lsig})} \\
  \denotesC{\goodType{\Gm}{\TyTkg{\lsig}}{}} &= \Gmodel{\Glued{\mathit{P}}(\denotesC{\lsig})} \quad \text{ discard syntax info}  \\
  % 
  \denotesC{\goodSig{\Gm}{\LSigEmp}{0}} &= "nil"\\ 
  \denotesC{\goodSig{\Gm}{\LSigAdd{\lsig}{s}{T}}{n+1}} &= (\denotesCC{A}, \denotesCC{s}, \denotesCC{T})::\denotesC{\lsig} \quad \text{ given } \goodTerm{\Gm, \TyTkg{\lsig}}{s}{A} \\ 
  \denotesC{\goodSig{\Gm}{\sub{\lsig}{\gm}}{n}} & \text{ is done by point-wise/component-wise substitution} \\
  \denotesC{\goodSig{\Gm}{\lsigproj{1}{\lsig}}{n}} &= "tl"~\denotesC{\lsig}\\ 
  \denotesC{\goodType{\Gm}{\lsigprojT{\lsig}}{}} &= \Gmodel{("hd"~\denotesC{\lsig})[0]} \quad \text{ take the first element in the tuple,...}\\ 
  \denotesC{\goodTerm{\Gm, \TyTkg{\lsigproj{1}{\lsig}}}{\lsigproj{s}{\lsig}}{\lsigprojT{\lsig}}} &= \Gmodel{("hd"~\denotesC{\lsig})[1]} \quad \text{  ... and discard syntax}\\ 
  \denotesC{\goodType{\Gm, \lsigprojT{\lsig}}{\lsigproj{2}{\lsig}}{}} &= \Gmodel{("hd"~\denotesC{\lsig})[2]}\\
  \denotesC{\goodTerm{\Gm}{\LkgEmp}{\TyLkg{\LSigEmp}}} &= \denotesC{\unit} \\
  \denotesC{\goodTerm{\Gm}{\LkgAdd{\lkg}{t}}{\TyLkg{\LSigAdd{\lsig}{s}{T}}}}(\gm)(\gm') &= (\denotesC{\lkg}(\gm)(\gm') , \Gmodel{\Glam{\denotesCC{t}}}(\gm)(\gm')) \\
  \denotesC{\goodTerm{\Gm}{\Tkg{\lkg}}{\TyTkg{\lsig}}} &= \denotesC{\unit}
  \quad \text{ when \goodSig{\Gm}{\lsig}{0}} \\
  \denotesC{\goodTerm{\Gm}{\Tkg{\lkg}}{\TyTkg{\lsig}}} &= \Gmodel{\Gpair{\Glued{\ell'}}{
    \colorbox{blue!17}{\Gsub{
    \colorbox{blue!9}{\Gsub{
    \colorbox{blue!1}{\denotesCC{\lkgproj{2}{\lkg}}}
    }{\GSubstExt{{\GSubstWeak{1}}}{s}}}
    }{\GSubstExt{\Glued{("id")}}{ \Glued{\ell'} }}}
    }}
  \\ &\text{ where } \Glued{\ell'} = \denotesCC{\Tkg{\lkgproj{1}{\lkg}}} 
  \\ &\text{ when } \denotesC{\goodSig{\Gm}{\lsig}{n+1}} = (A, s, T)::\_
  \\ &{~\begin{minipage}{.58\textwidth}\small
    In this definition, $\Gpair{\_}{\_}$ notates the glued interpretation of
    dependent tuple construction, $[\GSubstExt{\_}{\_}]$ notates the glued
    interpretation of substitution extension, and $\Gsub{\_}{\_}$ notates the
    glued interpretation of applying a substitution.
    \\
    The color boxes indicate the scopes of the two instances of $\Gsub{\_}{\_}$.
  \end{minipage}} \\[5pt]
%
%%The first complexity comes from the three ``bullets after comma'' notation. The way to interpret this notation is that, this ``$\GSubstExt{\_}{\_}$'' should be considered as a binary function requiring two input of glued interpretation. 
%
%%However, a careful reader will notice that, because of the overloading of the notation of dependent tuple construction and substitution extension, our glued notation is also overloaded. The first one ``$\Gpair{\Glued{\ell'}}{...}$'' should be the glued interpretation for dependent tuple, but the other two should be the one for substitution extension.
%
%%Similarly, the second complexity comes from the bullets after the square bracket, which as expected, is the glued interpretation for substitution. Again, ``$\Gsub{\_}{\_}$'' should be considered as a binary function consuming two glued interpretation, corresponding to the substitution operation ``$\sub{\_}{\_}$''.
%
%%Also note that, the only non-bullet-upscripted $s$ is from the pattern matching of the interpretation of $\lsig$.
%
  \denotesC{\goodTerm{\Gm}{\lkgproj{1}{\lkg}}{\TyLkg{\lsig}}}(\gm)(\gm') &= \denotesC{\ell}(\gm)(\gm')[0] \quad \text{ take the first element in the tuple} \\
  \denotesC{\goodTerm{\Gm, \lsigprojT{\lsig}}{\lkgproj{2}{\lkg}}{T}}(\gm_+)(\gm_+') &= ((\denotesC{\ell}(\pi_1{\gm_+})(\gm_+'[0]))[1])(\pi_2{\gm_+})(\gm_+'[1]) \\
  \denotesC{\goodWSig{\Gm}{\WSigEmp}{0}} &= "nil" \\
  \denotesC{\goodWSig{\Gm}{\WSigAdd{\wsig}{A}{B}}{n+1}} &= (\denotesCC{A} , \denotesCC{B}) :: \denotesC{\wsig}\\
  \denotesC{\goodWSig{\Gm}{\sub{\wsig}{\gm}}{n}} & \text{ is done by point-wise/component-wise substitution} \\
  \denotesC{\goodType{\Gm}{\wsigproj{j}{1}{\wsig}}{}} &= \Gmodel{(\text{ $j$-th element of }~\denotesC{\wsig})[0]}\\
  \denotesC{\goodType{\Gm, \wsigproj{j}{1}{\wsig}}{\wsigproj{j}{2}{\wsig}}{}} &= \Gmodel{(\text{ $j$-th element of }~\denotesC{\wsig})[1]}\\
  \denotesC{\goodWSig{\Gm}{\WSigSub{\wsig}}{n}} &= "tl"~\denotesC{\wsig}\\
  \denotesC{\goodTerm{\Gm}{\wcode{\wsig}}{\cU}}(\gm)(\gm')(t) &= \CWmodel~(\Gsub{\denotesCC{\wsig}}{\Glued{\gm}})~t \\
  \denotesC{\goodTerm{\Gm}{\Wsup{i}{\wsig}{a}{b}}{\El{\wcode{\wsig}}}}(\gm)(\gm') &= \CWsup~i~
  \colorbox{blue!10}{(\Gsub{\denotesCC{a}}{\Glued{\gm}})}~
  \colorbox{green!10}{(\Gsub{\denotesCC{b}}{{\Glued{\gm^\uparrow}}})} \\
  % CsTy~A~B~R &= {\GluedPi{A}{\GluedPi {\GluedPi{B}{\Gsub{R}{\GSubstWeak{2}}}} {\Gsub{R}{\GSubstWeak{2}}}}} \\
  \denotesC{\goodType{\Gm}{\CaseSig{"A"}{"B"}{"R"}}{}} &= 
  \Gmodel{\GluedPi{\denotesCC{"A"}}{\GluedPi {\GluedPi{\denotesCC{"B"}}{\Gsub{\denotesCC{"R"}}{\GSubstWeak{2}}}} {\Gsub{\denotesCC{"R"}}{\GSubstWeak{2}}}}} \\
  % CsTy~\denotesC{A}~\denotesC{B}~\denotesC{R}\\
We note that, the interpretation of $\Wsup{i}{\wsig}{a}{b}$ is defined by $\CWsup$ (defined below) will take three elements, $i$, a glued $(\Gsub{\denotesCC{a}}{\Glued{\gm}})$ and a glued $(\Gsub{\denotesCC{b}}{{\Glued{\gm^\uparrow}}})$.  As we mentioned earlier, $\Glued{\gm}$ is the equivalent form of $(\gm, \gm')$.

@@

\begin{align*}
  \text{we define } \RecSig{}{} &\text{ by induction on the signature, via } RS \\
  RS~"nil"~R &= \denotesCC{\LSigEmp} \\
  RS~((A, B) :: tl)~R &= \GLSigAdd{RS~tl~R}{\Glued{\pi_2}}{\GCaseSig{A}{B}{R}} \\ 
  \denotesC{\goodType{\Gm}{\RecSig{\wsig}{"R"}}{}} &= \Gmodel{RS~\denotesC{\tau}~\denotesC{"R"}} \\
  \denotesC{\Recproj{j}{\lkg}} &= \text{ take the $j$-th field from } \lkg 
\end{align*}
\begin{align*}
  \denotesC{\goodTerm{\Gm}{\Wrec{\wsig}{\lkg}{t}}{T}}(\gm)(\gm') = \CWrec \quad &\Gsub{\denotesCC{\wsig}}{\Glued{\gm}} \\ 
  & (\lambda w. \denotesC{"R"}(\gm)(\gm')(\Wrec{\sub{\wsig}{\gm}}{\sub{\lkg}{\gm}}{w}))\\
  &f^r\\ &\sub{t}{\gm}\\ 
  &(\denotesC{t}(\gm)(\gm')) 
\end{align*}
\begin{align*}  
  \text{ where } \quad f^r~j~\Glued{a}~b~b^c &= 
  \texttt{let}~\Glued{\rho}  \in \GTm{
    \colorbox{blue!15}{(\Glued{\cdot} \Glued{,} \colorbox{blue!5}{\Gsub{\Glued{B}}{\GSubstExt{\Glued{"id"}}{\Glued{a}}}})}
    }{
      \colorbox{green!10}{(\Gsub{\Gsub{\Glued{R}}{\Glued{\gm}}}{\GSubstWeak{1}})}
    } 
  \\
  &\texttt{ s.t.}~\Glued{\rho} \coloneq (\Wrec{\wsig}{\sub{\lkg}{\SubstComp{\gm}{\SubstWeak{1}}}}{b},b^c)~\texttt{ in } \\
  & \Gmodel{
    \Gsub{
      \colorbox{blue!27}{\Gapp{
        \colorbox{blue!18}{\Gsub{
          \colorbox{blue!9}{\Gapp{
            \colorbox{blue!0}{\GRecproj{j}{\Gsub{\denotesCC{\lkg}}{\Glued{\gm}}}}
            }}
          }{
            \GSubstExt{\GSubstId}{\Glued{a}}
          }}}}
      }{
        \GSubstExt{\GSubstId}{\Glam{\Glued{\rho}}}
      }
    }(\epsilon)(\star) \\
  & \quad 
   \text{ given } \goodTerm{\Gm}{\lkg}{\RecSig{\wsig}{"R"}} \\
   & \quad \text{ where }\Glued{R} = \denotesCC{"R"}, \Glued{B} = \Gwsigproj{j}{2}{\denotesCC{\wsig}}
\end{align*}

The semantic interpretations above are defined together with the following inductively defined indexed set $\CWmodel$ (with only one constructor $\CWsup$)
%
\begin{align*}
  "Inductive"~\CWmodel &: (\Glued{\wsig} \in \GWSig{i}{\denotesCC{\cdot}}{N}) \to \{ t : \goodTerm{\cdot}{t}{\El{\wcode{\wsig}}} \} \to \Set{i + 1} \quad "where" \\
    \CWsup &: j < N \to \Glued{a} \in \GTm{\Glued{\cdot}}{\Gwsigproj{j}{1}{\Glued{\wsig}}} \\
    & \to \Glued{b} \in (\GTm{
      \colorbox{blue!15}{(\Glued{\cdot} \Glued{,} 
      \colorbox{blue!5}{\Gsub{\Gwsigproj{j}{2}{\Glued{\wsig}}}{\SubstExt{\GSubstId}{\Glued{a}}}} )} 
      }{
        \colorbox{green!10}{\Gsub{\GEl{\Gwcode{\Glued{\wsig}}}}{\GSubstWeak{1}}}
        }) \\
    & \to \CWmodel~\Glued{\wsig}~\Wsup{j}{\wsig}{a}{b}
\end{align*}
and its eliminator $\CWrec$
\begin{align*}
  \CWrec \  &: (\Glued{\wsig} \in \GWSig{i}{\denotesCC{\cdot}}{N}) \to 
    (P : \{ t : \goodTerm{\cdot}{t}{\El{\wcode{\wsig}}} \} \to \Set{k})  \\
    & \to 
    [j < N \to  \Glued{a} \in \GTm{\Glued{\cdot}}{\Gwsigproj{j}{1}{\Glued{\wsig}}} \\ 
    & \quad \quad \to 
    \setc{b}{\goodTerm{({\cdot} , 
    \colorbox{blue!10}{\sub{\wsigproj{j}{2}{{\wsig}}}{\SubstExt{"id"}{{a}}}}
    ) }{b}{\sub{\El{\wcode{\wsig}}}{\SubstWeak{1}}}} \\ 
    & \quad \quad \to  \prod_{\Glued{\gm} \in \GSub{\Glued{\cdot}}{(\Glued{\cdot} \Glued{,} 
    \colorbox{blue!10}{\sub{\Gwsigproj{j}{2}{\Glued{\wsig}}}{\GSubstExt{\GSubstId}{\Glued{a}}}} )}} P~(\sub{b}{ \gm }) \\
    & \quad \quad \to P~(\Wsup{j}{\wsig}{a}{b}) ] \quad \text{ (square bracket here just to make things readable)} \\
    & \to \goodTerm{\cdot}{t}{\El{\wcode{\wsig}}} \to \CWmodel~\Glued{\wsig}~t \to P~t \\
  \CWrec \  & \Glued{\wsig}~P~f~t~(\CWsup~\Glued{a}~\Glued{b}) = f~\Glued{a}~b~(\lambda \Glued{\gm}. \CWrec~\Glued{\wsig}~P~f~(\sub{b}{\gm})~(\Gmodel{\Glued{b}}~\Glued{\gm}))
\end{align*}
